--- 
title: "Some thoughts on modelling in R"
author: "Alex Hayes"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
---

This document contains some initial thoughts about what a grammar of modelling might look like in R. The focus is on supervised and unsupervised learning in a frequentist setting (i.e. no worrying about posterior samples, etc).

# Motivation

```{r, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

Each model in R essentially lives in its own package and has a unique interface. This introduces a large amount of cognitive load on data analysts. For example, suppose we want to use KNN. We might do something like this:

```{r}
library(tidyverse)
library(rsample)

data <- initial_split(iris)

train <- training(data)
test  <- select(testing(data), -Species)

knn_preds <- class::knn(test = test,
                        train = select(train, -Species),
                        cl = train$Species,
                        k = 5)
```

But if we want to use naive Bayes, we might end up writing code that looks like this:

```{r}
nb_model <- e1071::naiveBayes(Species ~ ., data = train)
nb_preds <- predict(nb_model, newdata = test)
```

This has some problems:

  - `knn` generates predictions immediately on a test set, while `naiveBayes` creates a model object
  - For `knn` we have to pass arguments `cl` and `k` even though it would be reasonable to select `k` by cross-validation and `cl` could be more succinctly expressed as an outcome in a formula
  - `knn` and `naiveBayes` have different interfaces for specifying design matrices and outcomes
  - `knn` and `naiveBayes` both return factor predictions by default, but this might not be the case for other packages. If we want to class probabilities, we have to pass `prob = TRUE` to `knn` and `type = "raw"` to `predict.naiveBayes`, and the outputs are in entirely different formats.

That is, there isn't a consistent interface to the packages themselves. Additionally, the packages don't make use of a conceptual framework that makes it easy to think about modelling.

The goal is the document is provide a grammar of modelling that resolves both of these problems.
